Through the eyes of the teacher

### 2021-05-20 paper_1/paper_1_supplement_et_aoi.Rmd
update AOI plots

# prepare data (selected from AOI data)
et.raw.data<-read.table("./Aperol_pilot_AOI_glasses_metrics_session01.txt", dec=",", sep="\t", header=T)

@@

>>>>

# prepare data (selected from AOI data)
et.raw.data<-read.table("./data/Aperol_pilot_AOI_glasses_metrics_session01.txt", dec=",", sep="\t", header=T)

# convert into numeric
et.raw.data <- et.raw.data %>%  mutate(Total_duration_of_fixations = as.numeric(Total_duration_of_fixations),
                                       Average_duration_of_fixations = as.numeric(Average_duration_of_fixations),
                                       Number_of_fixations = as.numeric (Number_of_fixations),
                                       Total_duration_of_Visit = as.numeric(Total_duration_of_Visit))

@@

et.table <- et.raw.data %>%
  group_by(Group, AOI) %>%
  summarise("Mean Duration of Fixations" = mean(Total_duration_of_fixations),
            "Number of Fixations" = mean(Number_of_fixations),
            "Mean Duration of Visits" = mean(Total_duration_of_Visit))

view(et.table)

#FIXATIONS
# create a new column with name Total that gives the sum duration in msec of looking at all AOIs
et.raw.data <- et.raw.data %>% mutate(total_fixations = sum(Total_duration_of_fixations))

# create new columns that give proportion of the duration of looking at AOIs
# relative duration divided by total duration is the proportion
proportion.et.data <- et.raw.data %>% group_by(Group, AOI) %>% 
                                      mutate(proportion_fixations = Total_duration_of_fixations/total_fixations)

#VISITS
# create a new column with name Total that gives the sum duration in msec of visits in AOIs
et.raw.data <- et.raw.data %>% mutate(total_visits = sum(Total_duration_of_Visit))

# create new columns that give proportion of the duration of looking at AOIs
# relative duration divided by total duration is the proportion
proportion.et.data <- et.raw.data %>% group_by(Group, AOI) %>% 
                                      mutate(proportion_visits = Total_duration_of_Visit/Total)

### Plot data TOTAL FIXATIONS
total.fix.plot <- ggplot(et.raw.data, aes(x = AOI, y = Total_duration_of_fixations, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Total Duration of Looking at AOIs", x = "AOI")

total.fix.plot

### Plot data PROPORTIONS FIXATIONS
prop.fix.plot <- ggplot(proportion.et.data, aes(x = AOI, y = proportion_fixations, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Proportion of Looking at AOIs", x = "AOI")

prop.fix.plot

### Plot Number of Fixations
number.plot <- ggplot(et.raw.data, aes(x = AOI, y = Number_of_fixations, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Number of Fixations in AOI", x = "AOI")

number.fix.plot

### Plot data TOTAL VISITS
total.visit.plot <- ggplot(et.raw.data, aes(x = AOI, y = Total_duration_of_Visit, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Total Duration of Visits in AOIs", x = "AOI")

total.visit.plot

### Plot data PROPORTIONS VISITS
prop.visit.plot <- ggplot(proportion.et.data, aes(x = AOI, y = proportion_visits, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Proportion of Visits in AOIs", x = "AOI")

prop.visit.plot
